Verifying Cache Coherence Protocols for an infinite family of cache hierarchies

### 2014-02-06 paper/System.tex
this the the correct version

We have chosen as our concrete example a hierarchical MSI
protocol~\cite{MSI}. Logically, the system is organized in a tree
structure, with the root connected to the main memory and each leaf interfaced
with a processor (Figure~\ref{hier}). In the following, $\leaf(c)$ indicates
that a cache $c$ is a leaf, and $\parent(c,p)$ indicates that $p$ is the parent of
$c$.

@@

@@

Figure~\ref{childextra} shows transitions that happen in a non-root
cache due to the presence of \emph{voluntary} responses, which model eviction
from a cache to make room for a new location. This eviction usually
causes the permission state of the cache for that address to go to $\In$, while
we allow any downgrade to take place voluntarily.  We use the same \cpResp{}
FIFO for such a message. Such a voluntary response for an address can take
place only if the cache is not waiting for a response from its parent for
that address (ChildVolResp).

>>>>

We have chosen as our concrete example a hierarchical MSI
protocol~\cite{MSI}. Logically, the system is organized in a tree
structure, with the root connected to the main memory and each leaf interfaced
with a processor (Figure~\ref{hier}). The system is parameterized by the shape
of the tree, and each node can have any number of children independent of the
number in other nodes. In the following, $\leaf(c)$ indicates
that a cache $c$ is a leaf, and $\parent(c,p)$ indicates that $p$ is the parent of
$c$.

@@

We first give an intuition on how the transitions work in the common case.
A cache can decide, unsolicitedly \xxx{is this a word?}, to upgrade its state,
in which case it sends an upgrade request to its parent. The parent then makes
a local decision on whether to send a response to the requesting child or not
(based on its directory approximation, and its own state). If its own state is
lower the requested upgrade, then it can not handle the request. The parent
must instead, decide to upgrade its state -- the transition for doing so has
nothing to do with the incoming request.  Once the parent's state is not lower
than the requested upgrade, it makes sure that the rest of its children are
``compatible'' with the requested upgrade. If not, the parent must, send
requests to the uncompatible children to downgrade -- again the transition for
doing so has nothing to do with the incoming request. If the children are
compatible and its own state is higher, then the request can be handled and a
response is sent. Each of the transitions is explained in greater detail below.

@@

Figure~\ref{childextra} shows transitions that happen in a non-root cache due
to the presence of \emph{voluntary} responses, which model eviction of a
location from a cache to make room for a new location. This eviction usually
causes the permission state of the cache for that address to go to $\In$, while
we allow any downgrade to take place voluntarily.  We use the same \cpResp{}
FIFO for such a message. Such a voluntary response for an address can take
place only if the cache is not waiting for a response from its parent for that
address (ChildVolResp).
